\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeProject
    {E-Commerce Website: This website built for selling product online for my client.}
    {Tools: Wordpress ,Cms Platform,Css ,Html ,Php}
    {Nov 2024 - Dec 2024}
    {{}[\href{https://labelaj.com/}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
    \item Developed fully functional E-commerce website for Selling product online.
    \item Implemented Payment gateway System for Received payment from customer.
    \item Created Woocommerce , ensuring E-commerce Benifits.
\resumeItemListEnd
\resumeProject
    {Portfolio : My personal portfolio showcasing my skills, projects, and experiences.
}
    {Tools: Javascript , Reactjs , Typescript, Css , Html}
    {Oct 2024}
    {{}[\href{https://github.com/AlSabriBhuiyan0/Al-Sunny-Portfolio}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
    \item Developed with overflow feaures for Showcasing my Skills ,Project , and Expetiences.
    \item Implemented Typescript for Raw Output,
    achieving beautiful portfolio.
\resumeItemListEnd

\resumeProject
    {Recipe-Site-Traffic Analysis: Identify those likely to drive high traffic on the recipe platform.}
    {Tools: Python, Jupyter Notebook , Statistics , Data Visualization, Data Preprocessing , Machine Learning method} { May 2023}
{[\href{https://www.kaggle.com/code/alsabribhuiyan/recipe-site-traffic-analysis}{\textcolor{darkblue}{\faKaggle}}]}

\resumeItemListStart
    \item Integrated GradientBoostingClassifier Model and Logistic Regression Model to enhance model performance.
    \item Evaluated Model leading to Business metrics
    \item Research on traffic which is better for their platform.
\resumeItemListEnd

\resumeProject
    {Carbon Credit Stock Crypto Tracker: A comprehensive full-stack analytics platform for tracking and visualizing stock market data, crypto assets, and carbon credit transactions with AI-powered forecasting capabilities.}
    {Tools: React, Node.js, Express, PostgreSQL, Python, Prophet, ARIMA, Machine Learning, WebSocket}
    {2024}
    {{}[\href{https://github.com/AlSabriBhuiyan0/Carbon-credit-stock-crypto-tracker}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
    \item Implemented AI forecasting models (Prophet and ARIMA) for stock and crypto price predictions.
    \item Integrated real-time data from Yahoo Finance, crypto APIs, and UNFCCC for carbon credit tracking.
    \item Developed full-stack dashboard with portfolio management and real-time WebSocket updates.
    \item Created comprehensive analytics platform with role-based access control and authentication.
\resumeItemListEnd

\resumeProject
    {Treat Well Hospital Management System: A comprehensive hospital management system demonstrating advanced software engineering principles and database management concepts.}
    {Tools: Java, SQL, Database Design, Software Engineering}
    {2024}
    {{}[\href{https://github.com/AlSabriBhuiyan0/Cse311lproject}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
    \item Designed and implemented comprehensive database schema for hospital management operations.
    \item Developed application with advanced software engineering principles and best practices.
    \item Created system for managing patient records, appointments, and hospital administrative tasks.
\resumeItemListEnd

\resumeProject
    {Blockchain-based Token Project: A blockchain-based token project with local version implementation featuring token creation and smart contract functionality.}
    {Tools: Blockchain, Solidity, Web3, Smart Contracts, JavaScript, Ethereum}
    {2024}
    {{}[\href{https://github.com/AlSabriBhuiyan0/BrickToken-Local-version-updated}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
    \item Developed smart contracts for token creation and management using Solidity.
    \item Implemented decentralized application capabilities for digital asset management.
    \item Created blockchain-based token system with Web3 integration and local version support.
\resumeItemListEnd

\resumeProject
    {AI-powered Chatbot: An Android mobile application integrating Large Language Model (LLM) capabilities for intelligent interactions and AI-driven functionality.}
    {Tools: Android, Kotlin, Java, LLM, Machine Learning, Python, API Integration}
    {2024}
    {{}[\href{https://github.com/AlSabriBhuiyan0/LLM-Android-app-project-}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
    \item Integrated Large Language Model capabilities into Android mobile application.
    \item Implemented AI-powered features and natural language processing on mobile devices.
    \item Developed intelligent chatbot with API integration for real-time AI interactions.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8mm}

